\documentclass[11pt,a4paper,roman]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{black}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.75]{geometry}
\usepackage[dvipsnames]{xcolor}

\name{John}{Silva}
\address{Address first line}{Address second line}{}
\email{author@email.com}

\begin{document}

\recipient{}{}
\date{\today}
\opening{}
\makelettertitle{}

\textbf{Topic:} Response to reviewers \\
\textbf{Manuscript number:} SUBMIT-123456

\vspace{0.5cm}

Dear editor, Dear reviewers.

\justify{}
We wish to thank you for giving us the opportunity to submit a revised draft of
the manuscript “Article title” for publication in the
International Journal of Sciences. We appreciate the time and effort
that you dedicated to providing feedback on our manuscript, and we are grateful
for the insightful comments on and valuable improvements to our paper. In this
document, we try to address the issues raised as best as possible.

The most significant change made in the paper was due to the first comment of
Reviewer XXX, about the\ldots

In the subsequent paragraphs, we address each of the comments kindly presented
by the reviewers, with our answers written in blue. Similarly, the new version
of the manuscript, which follows this letter, has all modifications highlighted
in blue. All line and figure numbers cited below refer to the new version.

\vspace{0.5cm}

\textbf{Reviewer \#1:}

\vspace{0.3cm}
\begin{enumerate}
  \item First comment of Reviewer \#1.

  \vspace{0.3cm}
    \color{blue}
    Answer.
    \color{black}
  \vspace{0.3cm}

  \item Second comment of Reviewer \#1.

  \vspace{0.3cm}
    \color{blue}
    Answer.
    \color{black}
  \vspace{0.3cm}

\end{enumerate}

\vspace{0.5cm}

\textbf{Reviewer \#2:}
\begin{enumerate}
  \item First comment of Reviewer \#2.

  \vspace{0.3cm}
    \color{blue}
    Answer.
    \color{black}
  \vspace{0.3cm}

  \item Second comment of Reviewer \#2.

  \vspace{0.3cm}
    \color{blue}
    Answer.
    \color{black}
  \vspace{0.3cm}

\end{enumerate}

\vspace{0.5cm}

If the reviewers are not satisfied by our answers, we would be glad to
incorporate in our work changes resulting from further comments. Similarly, in
case the language is still not clear enough, we would be grateful if in the
next round of revisions, you point to us the specific sentences we should
improve.

Once again, we thank you for the time you put in reviewing our paper and look
forward to meeting your expectations.

\vspace{0.5cm}

Sincerely,

\vspace{0.5cm}

\begin{minipage}[t]{0.45\linewidth}
John Silva, PhD. \\
Senior Researcher \\
University of XXX
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\linewidth}
Second Author, PhD. \\
Senior Researcher \\
University of XXX
\end{minipage}

\vspace{0.5cm}

\begin{minipage}[t]{0.45\linewidth}
Third Author, PhD. \\
Senior Researcher \\
University of XXX
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\linewidth}
Forth Author, PhD. \\
Senior Researcher \\
University of XXX
\end{minipage}


\end{document}

